Finch: A Datastructure-Driven Array Programming Language

### 2024-03-20 sections/lang.tex
add some more variables and stuff
hmm

\begin{minipage}{0.6\linewidth}
    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchliteral(val \in \mathbb{V}) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    val
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchvalue(ex \in \mathbb{S}, type \in \mathbb{T}) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    ex :: type
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchtensor(name \in \mathbb{S}) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    name
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchindex(name \in \mathbb{S}) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    name
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchvar(name \in \mathbb{S}) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    name
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchextent(a \in E, b \in E) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    a : b
    \end{minted}
    \end{minipage}

    \noindent\begin{minipage}{.5\linewidth}
    \raggedleft $\finchcall(f \in E, args\ldots \in E) :=$~
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
    \begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
    f(args...)
    \end{minted}
    \end{minipage}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchaccess(tns \in E, idxs\ldots \in E) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
tns[idxs...]
\end{minted}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchassign(lhs \in A, op \in E, rhs \in E) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
tns[idxs...] <<op>>= rhs
\end{minted}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchloop(idx \in I, range \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
for idx = range; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchdefine(var \in V, val \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
let var = val; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchsieve(cond \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
if cond; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{.5\linewidth}
\raggedleft $\finchblock(bodies\ldots \in S) :=$~
\end{minipage}%
\begin{minipage}{.5\linewidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
begin; bodies... end
\end{minted}
\end{minipage}

>>>>

% Define variables for left and right minipage widths
\newlength{\leftwidth}
\setlength{\leftwidth}{.4\linewidth}
\newlength{\rightwidth}
\setlength{\rightwidth}{.6\linewidth}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\mathbb{V} :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
the set of all values.~
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\mathbb{S} :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
the set of all symbols.
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\mathbb{T} :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
the set of all types.
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $I :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
$\finchindex$
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $A :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
$\finchaccess$
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $V :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
$\finchvar$
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $E :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
$\finchliteral | \finchvalue | \finchindex | \finchvar | \finchextent | \finchcall | \finchaccess$
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $S :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
$\finchassign | \finchloop | \finchdefine | \finchsieve | \finchblock$
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchliteral(val \in \mathbb{V}) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
val
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchvalue(ex \in \mathbb{S}, type \in \mathbb{T}) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
ex :: type
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchtensor(name \in \mathbb{S}) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
name
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchindex(name \in \mathbb{S}) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
name
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchvar(name \in \mathbb{S}) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
name
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchextent(a \in E, b \in E) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
a : b
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchcall(f \in E, args\ldots \in E) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
f(args...)
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchaccess(tns \in E, idxs\ldots \in E) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
tns[idxs...]
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchassign(lhs \in A, op \in E, rhs \in E) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
lhs <<op>>= rhs
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchloop(idx \in I, range \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
for idx = range; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchdefine(var \in V, val \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
let var = val; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchsieve(cond \in E, body \in S) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
if cond; body end
\end{minted}
\end{minipage}

\noindent\begin{minipage}{\leftwidth}
\raggedleft $\finchblock(bodies\ldots \in S) :=$~
\end{minipage}%
\begin{minipage}{\rightwidth}
\begin{minted}[autogobble, linenos=false, fontsize=\normalsize]{julia}
begin; bodies... end
\end{minted}
\end{minipage}
